---
title: "group10-project2"
output: html_document
---

### Imports
```{r}
library(dplyr)
library(tidyr)
library(tidytext)
library(stringr)
library(ggplot2)
library(ggraph)
library(igraph)
library(RColorBrewer)
```

### Task 1
#### Reading DataFrame
```{r}
keywords <- read.csv('Keyword_data.csv')
keywords <- data.frame(lapply(keywords, str_to_title))
```

#### Converting to Adjacency Matrix
```{r}
# Stack all variables to find unique
stack_keywords <- stack(keywords)
# Calculate unique keywords
unique_keywords <- unique(stack_keywords$values)
# Create a weighted adjacency matrix
answer <- matrix(0, nrow=length(unique_keywords), ncol=length(unique_keywords))
colnames(answer) <- unique_keywords
rownames(answer) <- unique_keywords
# Logic to create weighted matrix
for(i in 1:length(keywords$Keyword.2)){
  temp <- unlist(keywords[i,])
  temp <- temp[!is.na(temp)]
  temp <- temp[temp != ""]
  keyword_list <- combn(temp,2)
  for(j in 1:length(keyword_list[1,])){
    rowind <- which(rownames(answer) == (keyword_list[1,j]))
    colind <- which(colnames(answer) == (keyword_list[2,j]))
    answer[rowind,colind] <- answer[rowind,colind]+1
    answer[colind,rowind] <- answer[colind,rowind]+1
  }
}
```

#### Converting to Network
```{r}
net <- graph_from_adjacency_matrix(answer, weighted = TRUE)
```

#### Top 10 Degrees
```{r}
degrees <- degree(net, mode='all')
top_10_degrees <- head(sort(degrees, decreasing = T), 10)
top_10_degrees
```

#### Top 10 Strengths
```{r}
strengths <- strength(net, mode='all')
top_10_strengths <- head(sort(strengths, decreasing = T), 10)
top_10_strengths
```

#### Top 10 Node Pairs by Weight
```{r}
node_pairs <- get.data.frame(net)
node_pairs <- node_pairs[order(-node_pairs$weight),]
head(node_pairs, 10)
```
#### Plotting Average Strength vs Degree
```{r}
averageWeight <- tapply(strengths, degrees, mean)
averageWeight <- data.frame(averageWeight)
avgWt_vs_deg <- cbind(degree=rownames(averageWeight), averageWeight)
row.names(avgWt_vs_deg) <- NULL
```

```{r}
plot(avgWt_vs_deg, type='p', pch = 1, main='Average Strength vs Degree', xlab='Degree', ylab='Average Strength')
lines(lowess(avgWt_vs_deg$degree, avgWt_vs_deg$averageWeight), col = "blue")
```

### Task 2
#### Reading csv file and stopwords
```{r}
twitter_df <- read.csv('2021.csv',header=T)
twitter_df$date <- strptime(twitter_df$date, format='%Y-%m-%d  %H:%M:%S') # converting date column
twitter_df$year <- format(twitter_df$date,"%Y") # adding year column
twitter_df <- twitter_df %>% 
                filter(language=='en', year %in% c("2017", "2018", "2019", "2020", "2021")) 
                # filtering by year greater than 2017 and language by English 

tweets_df <- data.frame(year=twitter_df$year, tweet=twitter_df$tweet)

stopwords <- read.table('stopwords.txt')
```

#### Cleaning Data
```{r}
tweets_df$tweet <- str_to_lower(tweets_df$tweet) # converting strings to lower case
tweets_df$tweet <- gsub("@\\w+", "", tweets_df$tweet) # removing mentions
tweets_df$tweet <- gsub("[[:digit:]]", "", tweets_df$tweet) # removing numbers

words_df <- tweets_df %>%
            unnest_tokens(word, tweet) %>% # tokennizing words
            filter(!word %in% stopwords$V1, # removing stopwords
                   !word %in% c("https", "t.co", "amp"), # removing urls and links
                   !grepl("^\\d+\\w\\d*", word),
                   !grepl("[^\x01-\x7F]+", word)) %>% 
            count(year, word, sort=T) # computing word count per year
```

#### Computing Word Frequencies
```{r}
total_words <- words_df%>% 
                  group_by(year) %>% 
                  summarize(total_words = sum(n))

words_df <- left_join(words_df, total_words)
words_df$frequency <- words_df$n/words_df$total_words # calculating word frequencies
```

#### Top 10 Words by Year
```{r}
year_df <- data.frame(year=numeric(0), word=character(0), frequency=numeric(0))
for (i in 2017:2021){
  temp_df <- head(subset(words_df, year==i),10)
  temp_df <- temp_df[, !names(temp_df) %in% c('n','total_words')]
  year_df <- rbind(year_df, temp_df)
}
```

##### Year 2017
```{r}
filter(year_df, year==2017)
```
##### Year 2018
```{r}
filter(year_df, year==2018)
```

##### Year 2019
```{r}
filter(year_df, year==2019)
```

##### Year 2020
```{r}
filter(year_df, year==2020)
```

##### Year 2021
```{r}
filter(year_df, year==2021)
```
#### Plotting Histograms of frequencies per year
##### Year 2017
```{r}
df2017 <- filter(words_df, year==2017)

ggplot(df2017, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=100) +
  xlim(NA, 0.02)
```

##### Year 2018
```{r}
df2018 <- filter(words_df, year==2018)

ggplot(df2018, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=100) +
  xlim(NA, 0.025)
```

##### Year 2019
```{r}
df2019 <- filter(words_df, year==2019)

ggplot(df2019, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=100) +
  xlim(NA, 0.02)
```

##### Year 2020
```{r}
df2020 <- filter(words_df, year==2020)

ggplot(df2020, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=100) +
  xlim(NA, 0.02)
```

##### Year 2021
```{r}
df2021 <- filter(words_df, year==2021)

ggplot(df2021, aes(frequency, fill = word)) +
  geom_histogram(show.legend = FALSE, bins=100) +
  xlim(NA, 0.02)
```

#### Zipf’s Law / log-log plots of word frequencies and rank
```{r}
freq_by_rank <- words_df %>% 
  group_by(year) %>% 
  mutate(rank = row_number(), 
         `term frequency` = frequency) %>%
  ungroup()

cols <- brewer.pal(5, "Spectral")

freq_by_rank %>% 
  ggplot(aes(rank, `term frequency`, color = year)) + 
  geom_line(size = 1.1, alpha = 0.8, show.legend = T) + 
  scale_x_log10() +
  scale_y_log10() +
  scale_color_manual(values = cols)
```

#### Creating Bigrams
##### Reading DataFrame again
```{r}
twitter_bigram_df <- read.csv('2021.csv',header=T)
twitter_bigram_df$date <- strptime(twitter_bigram_df$date, format='%Y-%m-%d  %H:%M:%S') 
twitter_bigram_df$year <- format(twitter_bigram_df$date,"%Y") 
twitter_bigram_df <- twitter_bigram_df %>% 
                filter(language=='en', year %in% c("2017", "2018", "2019", "2020", "2021")) 

tweets_bigram_df <- data.frame(year=twitter_bigram_df$year, tweet=twitter_bigram_df$tweet)

tweets_bigram_df$tweet <- str_to_lower(tweets_bigram_df$tweet) # converting strings to lower case
tweets_bigram_df$tweet <- gsub("@\\w+", "", tweets_bigram_df$tweet) # removing mentions
tweets_bigram_df$tweet <- gsub("[[:digit:]]", "", tweets_bigram_df$tweet) # removing numbers
```

##### Creating Bigrams DataFrame
```{r}
bigrams_df <- tweets_bigram_df %>%
            unnest_tokens(bigram, tweet, token = "ngrams", n = 2) 
```

##### Cleaning the data
```{r}
bigrams_df <- bigrams_df %>%
  separate(bigram, c("word1", "word2"), sep = " ")

bigrams_df <- bigrams_df %>%
                filter( !word1 %in% c("https", "t.co", "amp"), 
                        !word2 %in% c("https", "t.co", "amp"),
                        !grepl("^\\d+\\w\\d*", word1),
                        !grepl("[^\x01-\x7F]+", word1),
                        !grepl("^\\d+\\w\\d*", word2),
                        !grepl("[^\x01-\x7F]+", word2))

bigrams_df <- bigrams_df %>%
                filter(!word1 %in% stopwords$V1) %>%
                filter(!word2 %in% stopwords$V1)
```

##### Counting Bigrams
```{r}
bigrams_df <- bigrams_df %>% 
                count(year, word1, word2, sort = T)

bigrams_df <- bigrams_df[complete.cases(bigrams_df),]
```

##### Year 2017
```{r}
df2017 <- filter(bigrams_df, year==2017)
df2017 <- df2017[,2:4]

bigram_graph <- df2017 %>%
  filter(n > 2) %>% # filtering pairs with frequency less than 3
  graph_from_data_frame()

a <- grid::arrow(type = "closed", length = unit(.05, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```

##### Year 2018
```{r}
df2018 <- filter(bigrams_df, year==2018)
df2018 <- df2018[,2:4]

bigram_graph <- df2018 %>%
  filter(n > 3) %>% # filtering pairs with frequency less than 4
  graph_from_data_frame()

a <- grid::arrow(type = "closed", length = unit(.05, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```

##### Year 2019
```{r}
df2019 <- filter(bigrams_df, year==2019)
df2019 <- df2019[,2:4]

bigram_graph <- df2019 %>%
  filter(n > 3) %>%  # filtering pairs with frequency less than 4
  graph_from_data_frame()

a <- grid::arrow(type = "closed", length = unit(.05, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```

##### Year 2020
```{r}
df2020 <- filter(bigrams_df, year==2020)
df2020 <- df2020[,2:4]

bigram_graph <- df2020 %>%
  filter(n > 3) %>%  # filtering pairs with frequency less than 4
  graph_from_data_frame()

a <- grid::arrow(type = "closed", length = unit(.05, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```

##### Year 2021
```{r}
df2021 <- filter(bigrams_df, year==2021)
df2021 <- df2021[,2:4]

bigram_graph <- df2021 %>%
  filter(n > 1) %>%  # filtering pairs with frequency less than 1
  graph_from_data_frame()

a <- grid::arrow(type = "closed", length = unit(.05, "inches"))

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()
```
